Model LF

### 2022-12-15 Paper version rmd.Rmd
Commit

COMMENT> 
IDENTITY> wage_ds_t
EQ> wage_ds_t= wage_ds*(1+inflation_t) 
IF> SD1 >=1 & shock_wage_ds_model <= 0
IDENTITY> wage_ds_t
EQ> wage_ds_t= wage_ds*(1+inflation_t) 
IF> TSLAG(wage_gap1,1) > max_gap & SD1 >=1 & shock_wage_ds_model > 0 
IDENTITY> wage_ds_t
EQ> wage_ds_t= max_dp/(1-max_gap)
IF> TSLAG(wage_gap1,1) <= max_gap & SD1 >=1 & shock_wage_ds_model > 0 
IDENTITY> wage_ds_t
EQ> wage_ds_t= TSLAG(wage_ds_t,1)
IF> SD2 >= 1
IDENTITY> wage_ds_t
EQ> wage_ds_t= TSLAG(wage_ds_t,1)
IF> SD3 >= 1
IDENTITY> wage_ds_t
EQ> wage_ds_t= TSLAG(wage_ds_t,1)
IF> SD4 >= 1

@@

COMMENT> 
IDENTITY> prod
EQ> prod=prodk * (y/yk)
if> shock_prod_model <= 0
IDENTITY> prod
EQ> prod =  prod_ds +alpha_150 + alpha_151*SD1 + alpha_152*SD2 + alpha_153*SD3 - mean_prod
IF> shock_prod_model > 0

@@

COMMENT> 
IDENTITY> prodk
EQ> prodk=prod * (yk/y)
IF> shock_prod_model > 0

COMMENT> 
IDENTITY> prod_ds
EQ> prod_ds = prodk_ds * (y_ds/yk_ds)
IF> shock_prod_model <= 0
IDENTITY> prod_ds
EQ> prod_ds= prod_ds_shock
if> shock_prod_model > 0 & sens_3 <= 0
IDENTITY> prod_ds
EQ> prod_ds= prod_ds_sens
if> shock_prod_model > 0 & sens_3 > 0

IDENTITY> prodk_ds
EQ> prodk_ds=prod_ds * (yk_ds/y_ds)
IF> shock_prod_model > 0
IDENTITY> prodk_ds
EQ> prodk_ds=prod_ds * (yk_ds/y_ds)
IF> shock_lf_model > 0

@@

BEHAVIORAL> part1
TSRANGE 2006 2 2020 1
EQ> TSDELTALOG(part1) = beta_0 + beta_1*TSDELTALOG(TSLAG(part1,2)) + beta_2*TSDELTALOG(TSLAG(part1,3))  +beta_3*TSDELTALOG(TSLAG(kont_h_ratio,1)) +beta_4*TSDELTALOG(rw_ds)  +beta_5*TSDELTALOG(TSLAG(rw_ds,2)) +beta_6*TSDELTALOG(TSLAG(rw_ds,3))  + beta_8*LOG(TSLAG(part1,1))  + beta_9*log(TSLAG(rw_ds,1)) + beta_10*log(TSLAG(kont_h_ratio,1)) + beta_11*TSLAG(ur_ds,1)
COEFF> beta_0 beta_1 beta_2 beta_3 beta_4 beta_5 beta_6 beta_8 beta_9 beta_10 beta_11 
STORE> coe(16)

@@

COMMENT> Capital Stock with switches
IDENTITY> g
EQ> g = g*1
IF> shock_g_model <= 0
IDENTITY> g
EQ> g = g_shock
IF> shock_g_model > 0

@@

COMMENT> Capital Stock with switches
IDENTITY> pf
EQ> pf = pf*1
IF> shock_1_model <= 0
IDENTITY> pf
EQ> pf = pf_shock
IF> shock_1_model > 0

COMMENT> Capital Stock with switches
IDENTITY> pm_ds
EQ> pm_ds = pm_ds*1
IF> shock_1_model <= 0
IDENTITY> pm_ds
EQ> pm_ds = pm_ds_shock
IF> shock_1_model > 0

COMMENT> Capital Stock with switches
IDENTITY> iloan
EQ> iloan = iloan*1
IF> shock_2_model <= 0
IDENTITY> iloan
EQ> iloan = iloan_shock
IF> shock_2_model > 0

COMMENT> Capital Stock with switches
IDENTITY> idep
EQ> idep = idep*1
IF> shock_2_model <= 0
IDENTITY> idep
EQ> idep = idep_shock
IF> shock_2_model > 0

COMMENT> Capital Stock with switches
IDENTITY> ibd
EQ> ibd = ibd*1
IF> shock_2_model <= 0
IDENTITY> ibd
EQ> ibd = ibd_shock
IF> shock_2_model > 0

COMMENT> Capital Stock with switches
IDENTITY> iboa
EQ> iboa = iboa*1
IF> shock_2_model <= 0
IDENTITY> iboa
EQ> iboa = iboa_shock
IF> shock_2_model > 0

COMMENT> Lavet for at kunne støde til g 
IDENTITY> shock_3_model
EQ> shock_3_model = shock_3_model*1

COMMENT> Lavet for at kunne støde til g 
IDENTITY> shock_2_model
EQ> shock_2_model = shock_2_model*1

COMMENT> Lavet for at kunne støde til g 
IDENTITY> shock_1_model
EQ> shock_1_model = shock_1_model*1

COMMENT> Lavet for at kunne støde til g 
IDENTITY> shock_g_model
EQ> shock_g_model = shock_g_model*1

COMMENT> Lavet for at kunne støde til g 
IDENTITY> shock_prod_model
EQ> shock_prod_model = shock_prod_model*1

@@

COMMENT> Lavet for at kunne støde til g 
IDENTITY> shock_part_model
EQ> shock_part_model = shock_part_model*1

COMMENT> Lavet for at kunne støde til g 
IDENTITY> shock_wage_ds_model
EQ> shock_wage_ds_model = shock_wage_ds_model*1

COMMENT> Lavet for at kunne støde til g 
IDENTITY> shock_kuld_model
EQ> shock_kuld_model = shock_kuld_model*1

COMMENT> Lavet for at kunne støde til g 
IDENTITY> shock_lf_model
EQ> shock_lf_model = shock_lf_model*1

@@

  max_dp_shock = TIMESERIES(c(max_dp_shock),   
                       START=c(2005,2),FREQ=4),
  part1 = TIMESERIES(c(part1),   
                       START=c(2005,2),FREQ=4),

>>>>

COMMENT> 
IDENTITY> wage_ds_t
EQ> wage_ds_t= wage_ds*(1+inflation_t) 
IF> TSLAG(wage_gap1,1) > max_gap & SD1 >=1  
IDENTITY> wage_ds_t
EQ> wage_ds_t= max_dp/(1-max_gap)
IF> TSLAG(wage_gap1,1) <= max_gap & SD1 >=1  
IDENTITY> wage_ds_t
EQ> wage_ds_t= TSLAG(wage_ds_t,1)
IF> SD2 >= 1
IDENTITY> wage_ds_t
EQ> wage_ds_t= TSLAG(wage_ds_t,1)
IF> SD3 >= 1
IDENTITY> wage_ds_t
EQ> wage_ds_t= TSLAG(wage_ds_t,1)
IF> SD4 >= 1

@@

COMMENT> 
IDENTITY> prod
EQ> prod =  prod_ds +alpha_150 + alpha_151*SD1 + alpha_152*SD2 + alpha_153*SD3 - mean_prod

@@

COMMENT> 
IDENTITY> prodk
EQ> prodk=prod * (yk/y)

COMMENT>
IDENTITY> prod_ds
EQ> prod_ds= prod_ds_shock
if> sens_3 <= 0
IDENTITY> prod_ds
EQ> prod_ds= prod_ds_sens
if> sens_3 > 0

IDENTITY> prodk_ds
EQ> prodk_ds=prod_ds * (yk_ds/y_ds)

@@

@@

@@

@@

@@

  max_dp_shock = TIMESERIES(c(max_dp_shock),   
                       START=c(2005,2),FREQ=4),
